---
title: "Lab1"
author: "Tiana"
date: "2024-09-05"
output: "github_document"
---

# Load Packages
```{r}

library(haven)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggstatsplot)
library(psych)
library(bruceR)
library(ggsci)
library(datasauRus)

```

# First look of descriptive statistics 
```{r}

datasaurus_dozen %>% 
  group_by(dataset) %>%
  dplyr::summarize(mean_x    = mean(x),
      mean_y    = mean(y),
      std_dev_x = sd(x),
      std_dev_y = sd(y),
      corr_x_y  = cor(x, y)
    )


```

# Introduce GGplot
```{r}

ggplot(datasaurus_dozen, aes(x = x, y = y, colour = dataset))+
    geom_point()+ facet_wrap(~dataset)

dino<- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(dino, aes(x = x, y = y))+
    geom_point(color="#FF00FF")+ theme_void() + labs(title="Hi, I'm a DINO~")+ theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20, color = "pink"))

```



# Q1: What is the function of facet wrap? In what situation do you think you will use this function? 
It separates the dataset on one graph with a individual x-axis, y-axis, its label, and color. To use it when it comes to more than one x.


# Q2: The means, standard deviations, and correlations are pretty much the same, but the data pattern looks very different for each dataset. What is the implication here? 
Even they have the same mean, standard deviation, they may show different graphs, and always check the descriptive stats.
